

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins to maximize page space
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.65in}
\addtolength{\textheight}{1.25in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - tightened
\titleformat{\section}{
  \vspace{-7pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

% Tightened itemize margins
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, itemsep=0pt]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Shaurya Malhotra}} & Email: \href{mailto:malhotrashaurya11@gmail.com}{malhotrashaurya11@gmail.com}\\
  \href{https://github.com/Shauryam22}{GitHub:~github.com/Shauryam22} \\
  \href{https://www.linkedin.com/in/shaurya-malhotra-34405a26a}{LinkedIn:~linkedin.com/in/shaurya-malhotra-34405a26a} & Mobile: +91 821-871-7845 \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology Chennai}{Chennai, India}
      {Master of Science - Data Science;  GPA: 8.97}{July 2025 -- Expected July 2027}
      \resumeItemListStart
        \resumeItem{Courses}{Artificial Intelligence, Machine Learning, Regression and Predictive Modelling, Database Management, Data Structures, Analysis of Algorithms, Databases, Statistical Analysis, Data Visualization, Analytical Skills}
      \resumeItemListEnd
    \resumeSubheading
      {University of Delhi}{Delhi, India}
      {Bachelor of Science - Physics Hons;  GPA: 8.03}{July 2022 -- June 2025}
      \resumeItemListStart
        \resumeItem{Courses}{Analytical skills, Classical Mechanics, Quantum Mechanics, Statistical Mechanics, Mathematical Physics}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
        
\section{Skills Summary}
    \resumeSubHeadingListStart
    \resumeSubItem{Languages}{~~~~~~Python, SQL, Java, C, R}
    \resumeSubItem{Frameworks}{~~~~PyTorch, FastAPI, LLM, Scikit, Pandas, Jupyter, NumPy, Matplotlib, Seaborn, TensorFlow}
    \resumeSubItem{Tools}{~~~~~~~~~~~~~~Git, MLflow, Docker, DagsHub, PostgreSQL, MongoDB, Power BI, Tableau, MS-Excel, Latex}
    \resumeSubItem{Platforms}{~~~~~~~VS Code, IntelliJ, Leetcode, PyCharm}
    \resumeSubItem{Soft Skills}{~~~~~~~Time Management, Leadership, Writing, Public Speaking}
\resumeSubHeadingListEnd

\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Research Experience {\href{https://github.com/Shauryam22/Hybrid-GNN-x-Transformer.git}{\textcolor{blue}{[Link]}}}}{VIT Chennai} 
    { Developed a Hybrid GNN+Transformer AI/Human Text Detection}{Sept 2025 -- Feb 2026}
    \resumeItemListStart
        \resumeItem{Built from scratch}
          {Created a hybrid deep learning model to identify AI-generated code with \textbf{93.5\% accuracy}, significantly outperforming standard text-based classifiers.}
        \resumeItem{Building Architecture}
          {Engineered a dual-branch architecture that analyzes both the sequential "meaning" of code (Transformer) and its structural "shape" (Graph Attention Network).}
        \resumeItem{Fine Tuning}
          {Improved model performance by \textbf{54\%} by integrating a custom "Global Co-occurrence Graph" to capture complex programming syntax patterns.}
        \resumeItem{Metrics}
          {Achieved high-fidelity results with a \textbf{96.5\% precision rate}, ensuring human-written code is rarely misclassified as AI.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart


% AUTO-INSERT-PROJECTS-HERE


\resumeSubItem{Deployed Machine Learning Web App [\href{https://book-recommender-system-6a49.onrender.com/}{\textcolor{blue}{Website}}]}
  {Designed a personalized recommendation system by calculating cosine similarity across high-dimensional feature vectors, successfully mapping user preferences against a catalog of [5,000$+$] items. Built a responsive Flask web application to serve real-time ML predictions, reducing inference time by [30\%] through optimized Pandas data handling and NumPy vectorization.}

\resumeSubItem{Insurance Premium Predictor (FastAPI, Docker, ML)[\href{https://github.com/Shauryam22/Insurance_Premium_Prediction_API.git}{\textcolor{blue}{Link}}]}
  {Developed an end-to-end machine learning pipeline to predict insurance premiums based on demographic and health data. Engineered a high-performance REST API using \textbf{FastAPI} to serve real-time model inferences. Containerized the application and its dependencies using \textbf{Docker}, ensuring consistent deployment environments and demonstrating robust MLOps practices.}
% \resumeSubItem{AI Agent Simulation (Python, OOP) \href{https://github.com/Shauryam22/Agents-Based-Vacuum-Cleaner.git}{\textcolor{blue}{[Link]}}}
%   {Engineered a Python-based AI agent simulation using OOP principles, achieving a \textbf{25\% reduction} in algorithm runtime through optimized code; also improved code maintainability scores.}
% RESUME-PROJECT-END
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------------
\vspace{-3pt}
\section{Leadership \& Achievements}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Event Coordinator -- Climate \& Sustainability Hackathon}{Chennai, India}
      {VIT Chennai}{March 2026}
      \resumeItemListStart
        \resumeItem{Event Execution}
          {Successfully planned and conducted a multi-college hackathon focused on developing technology solutions for climate and sustainability challenges.}
        \resumeItem{Team Coordination}
          {Managed end-to-end logistics, event scheduling, and participation for 10 competing teams from various colleges, ensuring a seamless and competitive environment.}
      \resumeItemListEnd

    \resumeSubheading
      {Top 9 Finalists (out of 40 Teams)}{VIT Chennai}
      {Agrhinova Hackathon}{April 2026}
      \resumeItemListStart
        \resumeItem{Full-Stack Engineering}
          {Developed an end-to-end ag-tech web application in 24 hours, integrating a custom data-processing backend with an interactive frontend dashboard.}
        \resumeItem{Algorithmic Modeling}
          {Built a rule-based weighted scoring model to evaluate metrics and applied statistical smoothing to API data to visualize reliable, noise-free trends.}
        \resumeItem{Industry Pitch}
          {Pitched the fully functional prototype to industry leadership at BirdTech Solutions, demonstrating technical execution and business viability.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------CERTIFICATES-----------------
\vspace{-3pt}
\section{Certificates}
\resumeSubHeadingListStart
\resumeSubItem{Supervised Machine Learning (Stanford) \href{https://www.coursera.org/account/accomplishments/certificate/X4QH93PRGJ7N}{\color{blue}[Certificate]}}
{Mastered gradient descent and regularization. Implemented regression models from scratch using NumPy and Scikit-Learn.}

\resumeSubItem{What is Data Science? (IBM) \href{https://www.coursera.org/verify/YOUR_ID_HERE}{\color{blue}[Certificate]}}
{Explored the data science lifecycle and methodology. Focused on defining data-driven problems for industry-scale applications.}
\resumeSubHeadingListEnd

\end{document}